## MATRIX
## A matrix is a two-dimensional rectangular dataset. it can be created using a vector input to the matrix function

## matrix function
# data is entered columnwise (or do byrow=T)  
 1st arg: c(values of columns)  
 2nd arg: no. of rwos  
 3rd arg: no. of columns  

```{r}
A <- matrix(c(2,3,-2,1,2,2),3,2)
A
```

## byrow=T
```{r}

B <- matrix(c(2,3,-2,1,2,2),3,2,byrow=T)
B
y <- matrix(1:20,nrow=4,ncol=5)
y
```

## Naming Row and Columns > use dimnames arg of matrix function
```{r}
Rownames = c("A","B","C")
Colnames = c("x","y","z")
y = matrix(20:9,nrow=3,ncol=3,dimnames = list(Rownames,Colnames))
y
```
## Matrix Addtiton and Subtraction
```{r}

A <- matrix(c(5,4,1,0),2,2)
B <- matrix(c(1,4,-2,1),2,2)
```
## elemnetwise mul *
## matrix mul %*%
```{r}

A+B
A*B
A %*% B
```

## Transpose of matrix > AT <- t(A)

```{r}
A
AT <- t(A)
AT
```

## diag , zero, ones, eye



## STATISTICS

```{r}
A

colSums(A)
colMeans(A)
mean(A)
```

## append matrice columnwise
```{r}
cbind(A,B)
```
## append matrice rowise
```{r}
rbind(A,B)
```

