---
title: "R Notebook"
output: html_notebook
---
# Data frame
Data frame is a table of information like an Excel Sheet
Contains rows and columns containing different peices of information
Each column may be in different data types

ID    NAME  MARKS
1     Ramu   50
2     Raju   40
3     Ravi   25

```{r}
df <- data.frame(Id = c(1,2,3), Name = c("Ramu","Raju","Ravi"), Marks = c(50,40,25))
df
```
   gender   ht  wt
1   M     172.0 91
2   M     186.5 99
3   F     165.0 74

```{r}
df <- data.frame(gender = c("M","M","F"),ht=c(172.0,186.5,165.0),wt=c(91,99,74))
df
```
get heights only
```{r}
df$ht
```
## get weight of 2nd person
```{r}
df$wt[2]
```
## names of columns
```{r}
names(df)
```
## rownames
change index names
```{r}
rownames(df) <- c("Alpha","Beta","Charlie")
df
```

# Expanding Data Frames
##> Adding new column
```{r}
df$age <- c(28,55,43)
df
```

## Adding new rows
new additions should also be a Data Frame
```{r}
m2 <- data.frame(gender = c("M","F"),ht = c(170,166),wt = c(68,72),age = c(38,22))
rownames(m2) <- c("Delta","Epsilon")
df2 <- rbind(df,m2)
df2
```
# mtcars
```{r}
df = data.frame(mtcars)
df
```
# Basic Operations
## Head
```{r}
head(df)
```
## Dimensions
```{r}
dim(df)
```
## Summary
```{r}
summary(df)
```
## Subsetting
rowwise
```{r}
df[4:10,]
```
column wise
```{r}
df[,c(2,6)]
```
OR
```{r}
df[c("mpg","cyl")]
```
```{r}
df[,c(-3)]
```
## Subsetting based on conditions
```{r}
subset(df,mpg>18)
```
more than one conditions
```{r}
subset(df,mpg>16 & cyl>5)
```
exclude columns and subset with conditions
```{r}
subset(df,cyl>5&mpg>20,select=c(-mpg,-cyl))
```




