---
title: "lab8statistics"
author: "Yasir Ahmad"
date: "2023-10-31"
output: html_document
---

# Basic Statistics in R
## Measurement of dispersion
* range  
* inter-quartile range  (IQR) 
* standard deviation  
* distance

## Outliers
```
Outliers(lower) = Q1 - 1.5*IQR
Outliers(upper) = Q3 + 1.5*IQR
```
Use box plot to visualize the outliers.

## Coefficient of Variation
```
CV = (sd/mean)*100
```
## Skewness
* Positively Skewed
* Negatively Skewed

```
Skewness = (mean-mode)/sd 
         = 3(mean-median)/sd
```
```
Skewness = 0 -> symmetric  
         = -0.5 to +0.5 -> approximately symmetric  
         = -1 to +1 -> moderately skewed  
         = <-1 to >+1 -> highly skewed  
```      
         
         
## Kurtosis
* mesokurtic = 0
* laptokurtic > 3
* platykurtic <3

## covariance and correlation
Relationship between two attributes

if cov > 0 => directly proportional  
if cov <0 => inversely proportional
if cov 0 => random

## correlation matrix
Heatmap of all the correlation coefficients between every possible pair of variables

# Code
```{r}
library(MASS)
```

```{r}
newg = na.omit(geyser)
View(newg)
```

```{r}
newf = na.omit(faithful)
View(newf)
```


## Calculate statistics
### MEAN
```{r}
mu = mean(newf$eruptions)
cat("Mean of eruptions is",mu)
```
### Median
```{r}
Q2 = median(newf$eruptions)
cat("Median of eruptions is",Q2)
```
### Quartiles
```{r}
quantile(newf$eruptions)
```
* 80 percentile and 75 percentile
```{r}
quantile(newf$eruptions,c(0.8,0.75))
```
### IQR
```{r}
iqr = IQR(newf$eruptions)
cat("Inter quartile range of eruptions is ",iqr)
```

### Range
```{r}
quantile(newf$eruptions,1)-quantile(newf$eruptions,0)
#or
range = max(newf$eruptions) - min(newf$eruptions)
cat("range of eruptions is ",range)
```

### var
```{r}
vr = var(newf$eruptions)
cat("variance of eruptions is ",vr)
```

### sd
```{r}
s = sd(newf$eruptions)
cat("standart deviation of eruptions is ",s)
```

#library e1071
`e1071` is required for following operations
```{r}
library("e1071")
e = newf$eruptions
```


### central moment
order = k =3
```{r}
mu3 = moment(e,order=3,center=TRUE)
cat("Central moment of order 3 is ",mu3)
```

### skewness
```{r}
sk = skewness(e)

if(sk > 0){
  print("Positive (RIGHT) skewed")
}else if(sk < 0){
  print("Negative (LEFT) skewed")
}

if(sk == 0){
  cat("Perfectly symmetric, skewness =",sk)
}else if(-0.5<sk && sk<0.5){
  cat("Approximately skewed, skewness=",sk)
}else if(-1<sk && sk<1){
  cat("Moderately skewed, skewness=",sk)
}else{
  cat("Highly skewed, skewness=",sk)
}
```

### kurtosis
```{r}
k = kurtosis(e)
if(k == 3){
  cat("Mesokurtic, kurtosis =",k)
}else if(k>3){
  cat("Leptokurtic, kurtosis =",k)
}else{
  cat("Platykurtic, kurtosis =",k)
}
```
### correlation and covariance
```{r}
covar = cov(e,newf$waiting)
corr = cor(e,newf$waiting)

if(covar==0){
  cat("No relation among variables, covariance =",covar)
}else if (covar>0){
  cat("Variables are positively related(directly proportional), covariance =",covar)
}else{
  cat("Variables are negatively related(inversely proportional), covariance =",covar)
}
cat("\n")
if(corr==0){
  cat("No relation among variables, correlation =",corr)
}else if (corr==1 || corr==-1){
  cat("Variables are perfectly related, correlation =",corr)
}else if (corr>0){
  cat("Variables are positively related(directly proportional), correlation =",corr)
}else{
  cat("Variables are negatively related(inversely proportional), correlation =",ccrr)
}
```








