---
title: "lab10practice"
author: "Yasir Ahmad"
date: "2023-11-07"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Visualisation practice
Use the newsurvey data obtained by cleaning "na" values in survey data of MASS package to
do the following:   
```{r}
library(MASS)
library(ggplot2)
newsurvey = na.omit(survey)
```

1. Plot a bar graph for the number of male and female participants in the survey. Provide
the title as “Male and Female participants”, y-axis label as “frequency” and specify
the colours for the bars.   
```{r}
freq = table(newsurvey$Sex)
barplot(freq,main="Male and Female participants", ylab="frequency",col=c('red','blue'))
```

2. Plot a bar graph for the number of left handers and right handers in the survey.
Provide the title as “Left Handers and Right Handers”, y-axis label as “count” and
specify the colours for the bars  
```{r}
freq = table(newsurvey$W.Hnd)
barplot(freq,main="Left Handers and Right Handers",ylab = "count", col=c("red","blue"))
```

3. Plot the distribution between male left handers and female left handers using bar
chart. Provide the title as “Female Left Handers and Male Left Handers , y-axis label
as “count” and specify the colours for the bars.  
```{r}
library(dplyr)
lft_hnders = filter(newsurvey,newsurvey$W.Hnd=="Left")
freq = table(lft_hnders$Sex)
barplot(freq, main="Female Left Handers and Male Left Handers", ylab="count",col = c('green','blue'))
```

4. Draw the histogram of age distribution with the title as „Age distribution‟ and xlabel
as „Age range‟ and ylabel as „frequency‟.
```{r}
hist(newsurvey$Age,main="Age Distribution",xlab="Age range",ylab="frequency")
```

5. Reveal the relationship between the age and writing hand span using scatter plot.
```{r}
plot(newsurvey$Wr.Hnd,newsurvey$Age)
```

6. Draw the boxplot for pulse rate to analyse the five summary statistics. Provide
appropriate title and label.
```{r}
boxplot(newsurvey$Pulse,main="boxplot of pulse rate")
summary(newsurvey$Pulse)
```
7. Draw the distribution of smoking habits of male left handers using pie chart.
```{r}
m_L = filter(lft_hnders,lft_hnders$Sex=="Male")
freq = table(m_L$Smoke)
pie(freq)
```

Read iris.csv or weather.csv
```{r}
data = iris
```
* Apply various visualization techniques.
```{r}
plot(iris$Sepal.Length,iris$Sepal.Width, main="Sepal length vs Sepal width")
```
* Perform correlation analysis and state the inferences
```{r}
plot(iris, main="Finding correlations using multiple scatter plot")
```
```{r}
slen_swid = cor(iris$Sepal.Length,iris$Sepal.Width)
slen_plen = cor(iris$Sepal.Length,iris$Petal.Length)
slen_pwid = cor(iris$Sepal.Length,iris$Petal.Width)
swid_plen = cor(iris$Sepal.Width,iris$Petal.Length)
swid_pwid = cor(iris$Sepal.Width,iris$Petal.Width)
plen_pwid = cor(iris$Petal.Length,iris$Petal.Width)

slen_swid
slen_plen 
slen_pwid 
swid_plen
swid_pwid
plen_pwid
```
therefore Sepal length and Petal length are positively correlated, Sepal length and Petal width are positively correlated and Petal length and Petal width are positively correlated  


* Identify outliers
```{r}
boxplot(iris,main="Finding outliers")
```


*   Plot the frequency table
```{r}
freq = table(iris$Species)
pie(freq)
```































