---
title: "lab10visualization"
author: "Yasir Ahmad"
date: "2023-11-07"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Visualization libraries
* Base Graphics  
* ggplot2  
* grid Graphics  
* lattice Graphics  

```{r }
data = airquality
View(data)
```


## Basic plots
### plot()

```{r}
plot(data$Ozone)
```

### Scatterplot
```{r}
plot(data$Ozone,data$Wind)
```

```{r}
freq = table(data$Month)
freq
plot(freq)
```

#### When the scatter plot is used with entire dataset, a matrix of scatterplot is obtained which is a correlation matrix of all the columns
```{r}
plot(data)
```

### Barplot
```{r}
barplot(data$Ozone,main="Ozone levels")
```
```{r}
barplot(data$Ozone,main="Ozone levels",horiz=TRUE)
```

### Histogram
```{r}
hist(data$Solar.R)
```



### Box plot
```{r}
boxplot(data$Ozone)
```
```{r}
boxplot(data[1:4],main="Multiple Box plot")
summary(data[1:4])
```

## ggplot
`library(ggplot2)`
mandatory attributes
* Data
* Aesthetics
* Geometrics

other attributes are facets,statistics,coordinates,themes
```{r}
library(ggplot2)
```

### common plots

**Scatter plot** geom_point  
**Bar plot** geom_bar  
**Histogram** geom_histogram  
**Linechart** geom_line  
**ploygon** geom_ploygon  


## ggplot() - Scatterplot
```{r}
ggplot(iris, aes(x=Sepal.Length,y=Petal.Length))+geom_point()

ggplot(data=mtcars,aes(x=wt,y=mpg))+geom_point()
```

```{r}
ggplot(iris, aes(x=Sepal.Length,y=Petal.Length, col=Species))+geom_point()
```

```{r}
ggplot(iris, aes(x=Sepal.Length,y=Petal.Length,col=Species,shape=Species))+geom_point()
```

```{r}
ggplot(iris, aes(x=Sepal.Length,y=Petal.Length,col=Species))+geom_point() +geom_smooth()
```

## ggplot() - Bar plot
```{r}
ggplot(mtcars,aes(x=gear))+geom_bar()
```

## ggplot() - HIstogram
```{r}
ggplot(mtcars,aes(x=mpg))+geom_histogram()
```

## ggplot() - Box plot
```{r}
ggplot(mtcars,aes(x=as.factor(cyl),y=mpg))+geom_boxplot()
```
`












