---
title: "lab7controlPractice"
author: "Yasir Ahmad"
date: "2023-10-28"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
# Questions

## 1 Write a program in R to find the sum of first ‘n’ Fibonacci numbers
```{r}
n = readline("Enter the value of n: ")
n = as.integer(n)
fibo = c(0,1)
sum = 1
for(i in 3:n){
  fibo[i] = fibo[i-1] + fibo[i-2]
  sum = sum + fibo[i]
}

cat("sum of",n,"fibonacci numbers is",sum)
```

## 2 Print the number of vowels and consonants present in your name.
```{r}
name = readline("Enter name: ")
name = strsplit(name,"")[[1]]
Vcount = 0
Ccount = 0
V = c('a','e','i','o','u')
for(i in name){
  #print(i)
  if(i %in% V){
    Vcount = Vcount + 1
  }
  else{
    Ccount = Ccount + 1
  }
}
print(name)
cat("Number of vowels: ",Vcount,"\n")
cat("Number of consonants: ",Ccount)
```

## 3 Given a number, write r script to print the pairwise factors of the given number
```{r}
x = readline("Enter number: ")
x = as.integer(x)
for(i in 1:x){
  if(x%%i==0){
    cat(i,",",x/i,"\n")
  }
}
```

## 4 Write a program to generate any 10 random numbers between 10 and 100 and then create two vectors to store the odd and even numbers.
```{r}
EvnV = c()
OddV = c()
for(i in 1:10){
  r = sample(10:100,1)
  print(r)
  if(r%%2==0){
    EvnV = append(EvnV,r)
  }
  else{
    OddV = append(OddV,r)
  }
}
cat("Even numbers:",EvnV,"\n")
cat("Odd numbers: ",OddV)
```

## Password Validation
Find the strength of the given password. The password is strong if it satisfies all the below
conditions. A moderate password is one that satisfies first three conditions and has length at
least 6, otherwise password is week.
* It contains at least one lowercase English character.
* It contains at least one uppercase English character.
* It contains at least one special character. The special characters are: !@#$%^&*()-+
* Its length is at least 8.
* It contains at least one digit.

```{r}
pswd = readline("Enter Password: ")
pd_st = strsplit(pswd,"")[[1]]
Co = c(FALSE,FALSE,FALSE,FALSE,FALSE)
Co[4] = length(pd_st)>7 
for(i in pd_st){
  if(i %in% c("!","@","#","$","%","^","&","*","(",")","-","+")){
    Co[3] = TRUE
  }
  if(i %in% letters){
    Co[1] = TRUE
  }
  if(i %in% LETTERS){
    Co[2] = TRUE
  }
  if(i %in% c("1","2","3","4","5","6","7","8","9","0")){
    Co[5] = TRUE
  }
}
if(sum(Co)==5){
  print("Strong Password")
}else {
  if((sum(Co[1:3])==3) && (length(pswd)>5)){
  print("Moderate Pasword")
  }else{
    print("Weak Password")
  }
}

```



