---
title: "Rdplyr practice"
output: html_notebook
---
# Data Manipulation using dplyr package
*Note: use mtcars dataset*  

### 1. Display all the variables of data with some portion of the data for each variable that can be fit on a single line.
```{r}
car = mtcars
glimpse(car)
```

### 2.Display all the observations
```{r}
car
```

### 3.Display any 5 observations randomly.
```{r}
sample_n(car,5)
```

### 4.Display only a fraction of observations randomly.
```{r}
sample_frac(car,0.3)
```

### 5.Display only the MPG column.
```{r}
select(car,mpg)
```

### 6.Display the variables that starts with the letter ‘d’
```{r}
select(car,starts_with('d'))
```

### 7.Displays data in the columns from MPG to DISP without the CYL attribute.
```{r}
select(car,mpg:disp,-cyl)
```

### 8.Display all records whose HP values are more than 125 and MPG less than 15.0
```{r}
filter(car,hp>125,mpg<15)
```

### 9.Include a new attribute NV by adding WT and MPG together.
```{r}
mutate(car,nv = wt+ mpg)
```

### 10.Display the maximum and minimum HP value.
```{r}
summarize(car,min_hp=min(hp),max_hp=max(hp))
```

### 11.Filter all the data with HP greater than 125 and arrange them in increasing order of MPG.
```{r}
car %>%
  filter(hp>125) %>%
  arrange(mpg)
```

### 12.Calculate the average WT for each unique value in the AM column for mtcar data having HP > 125
```{r}
car %>%
  filter(hp>125)  %>%
  group_by(am) %>%
  summarize(avg_wt = mean(wt))
```
